Stochastic Wind Power Forecasting

### 2020-02-07 LaTeX_code/paper/paper_1line.tex
Added captions

Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Two samples from the Uruguayan of 2018. Each sample compromises of two 72-hour paths. In yellow is an hourly wind power production forecast. In blue is the actual wind power production recorded in 10 minute intervals. {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
  \caption{We see that forecast errors exhibit skewness near the boundries (i.e. low and high power production regimes.). Low power is when produced power is less than $0.3$, mid power is when it is between $0.3$ and $0.6$ and high power when is larger than $0.6$.   {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
  \caption{We observe that skewness has been greatly reduced after the Lamperti transformation. This motivates us to use a Gaussian transition density as a proxy density.  {\color{red} New figures with 2019 Uruguayan dataset.}}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
  \caption{Transitions.}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
  \caption{Transitions after the Lamperti transform.}
  \label{fig:skew_after_lamperti}
\end{figure}
%---END SECTION 1---

>>>>

{\color{red} Show with plots as the use of wind and solar power is increasing.}\\
Reliable wind power generation forecasting is crucial for the following applications (see, for example, \cite[5]{gieb}, \cite[162]{chang}, \cite{zhbo}):
\begin{itemize}
\item Allocation of energy reserves such as water levels in dams or oil, and gas reserves.
\item Operation scheduling of controlable power plants.
\item Optimization of the price of electricity for different parties such as electric utilities, Transmission system operator (TSOs), Electricity service providers (ESPs), Independent power producers (IPPs), and energy traders.
\item Maintenance planning such as that of power plants components and transmission lines.

@@

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/5.eps}
  \includegraphics[width=60mm,scale=1]{plots/245.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/661.eps}
  \includegraphics[width=60mm,scale=1]{plots/805.eps}
  \caption{Four samples from the Uruguayan data of 2019. Each sample compromises of two 24-hour paths. In blue is an hourly wind power production forecast. In orange is the actual wind power production recorded in 10 minute intervals from the company ADME.}
  \label{fig:sample_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_6.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_6.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_6.eps}
  \caption{We see that forecast errors exhibit skewness, which is exaggerated as a consequence of curtailing in the production. Low power is when produced power is in $[0,0.3]$, mid-power is when it is in $(0.3,0.6]$, and high power when it is in $(0.6,1]$. We have a total of 363 days to use.}
  \label{fig:skew_data}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP.eps}
  \caption{We observe that skewness has been reduced after removing the days with curtailing. We have a total of 255 days with no curtailing.}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t.eps}
  \caption{Transitions in error between forecast and real production. We can observe that they are not totally centered around zero.}
  \label{fig:skew_after_lamperti}
\end{figure}

\begin{figure}
  \includegraphics[width=60mm,scale=1]{plots/LP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/MP_t_LP.eps}\\
   \includegraphics[width=60mm,scale=1]{plots/HP_t_LP.eps}
  \includegraphics[width=60mm,scale=1]{plots/AP_t_LP.eps}
  \caption{Transitions after the Lamperti transform. The transitions now present a normal Gaussian shape. This effect motivates the use of Gaussian proxies to approximate the process after using the Lamperti transform.}
  \label{fig:skew_after_lamperti}
\end{figure}
%---END SECTION 1---
